### 2017-06-03 paper/documents/0.abstract.tex
- update paper

This is abstract\cite{eggert2015classification}

>>>>

The state of the art, computer games are big business, which is also reflected in the growing interest in competitive gaming. \textit{Multi-player online battle arena} games are the most successful games. Every players have own specific roles in this team based game. \textit{Dota 2} is the most popular for this games. This paper analyzing player roles and their behavior using \textit{supervised machine learning} and also investigates the applicability of feature normalization to enhance accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files. Using attribute evaluation techniques, we are able to reduce a larger set of candidate attributes down to a manageable number. \textit{Random Forest} the decision trees algorithm is the most stable and best performing classifier in our results.

### 2017-06-03 paper/documents/1.introduction.tex
- update paper

Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in Dota 2, the most popular MOBA game.

>>>>

Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in \textit{Dota 2}, the most popular MOBA game. Such information could be useful for game designer to better understand how their game design influences emergent gameplay and player behavior but also for players, both casual and professional, who want to analyze their own performance or who want to learn from the others. It could also support casters and moderators in commentating and presenting matches. Furthermore, this research might hold implications for social and other research concerned with (human behavior in) games. While ML has been applied to games and traditional sports, most works are either interested in questions like spatial behavior, trying to predict the match outcome, or otherwise trying to correlate performance to certain events or behaviors. In contrast, we aim at building a classifier that is largely independent of individual players performance and that is also not tied to the overall match outcome but that is able to identify a player's role in term of the non-formally defined roles established as common grounds within the \textit{Dota 2} or MOBA community.

### 2017-06-03 paper/documents/2.background.tex
- update paper

\textit{Dota 2} is team based game in Multi-player Online Battle Arena (MOBA). It is divided by two areas, the Dire and the Radiant. Each team have five players. Every player will choose their hero in pre-match games. Currently, there is 113 heroes, 166 current items. Dota2 game design is separated the heroes with three types. The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type. Every heroes have own specialty and weakness. The items can be combine into upgrade-able item which is will give more status in heroes abilities.

@@

Dota 2 map layout split into three lanes. Each lanes has three defensive towers. the Dire lanes and the Radiant lanes are quite different. the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane. The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane. And the middle lane will remain same.

>>>>

\textit{Dota 2} is team based game in \textit{Multi-player Online Battle Arena} (MOBA). It is divided by two areas, the \textit{Dire} and the \textit{Radiant}. Each team have five players. Every player will choose their hero in pre-match games. Currently, there is 113 heroes, 166 current items. \textit{Dota 2} game design is separated the heroes with three types. The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type. Every heroes have own specialty and weakness. The items can be combine into upgrade-able item which is will give more status in heroes abilities.

@@

\textit{Dota 2} map layout split into three lanes. Each lanes has three defensive towers. the Dire lanes and the Radiant lanes are quite different. the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane. The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane. And the middle lane will remain same.

### 2017-06-03 paper/documents/4.experiment.tex
- update paper

\subsection{Attribute Construction and Evaluation}
\label{sec:attconsandeval}
Attributes for evaluation is presented in table 1.

\subsection{Space and Movement}
\label{spaceandmovement}
Most of player roles depend on the lane (see figure x) which is the most active in the early game.

>>>>

\subsection{Attribute Construction and Evaluation}
\label{sec:attconsandeval}
Attributes for evaluation is presented in table 1. While some attributes correspond directly to summary data, attributes that capture positional information the fighting behavior require more complex processing of the replay data. Different attribute filters implemented in the Java library WEKA \cite{hall2009weka} to determine the best set of attributes. Our results with the \textit{WtrapperSubsetEval} class with best-first search are presented in table 1. We have chosen this algorithm for our nal attribute selection because it resulted in the highest accuracy with our labeled data set. For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy. In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files. They can be grouped into ve rough categories: space and movement, early ganks, team fights, support items, and damage types. Not all of the attributes we describe in this section were finally chosen to be used for classification within this work but they might prove valuable for future works.

\subsection{Space and Movement}
\label{spaceandmovement}
Most of player roles depend on the lane (see figure x) which is the most active in the early game. Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.
